---
title: "Fitbit_Part1"
author: "Litta Rizki A"
date: "3/8/2022"
output: html_document
---

This markdown was part of how I used R to do my research.
The rationale for including parts in each markdown was so that I could keep track of my R learning, which includes:


* how I rewrote the code

* how I dive further into the data to find answers to my questions about it


Let's get this party started, shall we?

## IMPORTING PACKAGES & DATA

###Packages
```{r, results='hold', warning=FALSE, class.source="bg-success"}

library(skimr)
library(tidyverse)
library(lubridate)

```

###Data
```{r, results='hold', class.source="bg-success"}
dailydata <- read_csv("dailyActivity_merged.csv")

head(dailydata)
```

## EDA

It's better to **know your data** before we start manipulating or plotting the data. which consists of:

* What data type is it?
* How many columns and rows?

I'm going to use the str() function for this.

```{r, message=FALSE, class.source="bg-success"}
str(dailydata)
```

As you can see, we've already identified our first issue, which is **the data type**. It was classified as "num" in the Id column, for example. **If we allow this to happen, it will be difficult to manipulate data** based on the Id.

Second, instead of being classified as "Date," the ActivityDate is now classified as "character," which will lead to data bias in the future if we allow both of those to slide.

So, let's convert the data type to a more proper.

```{r, message=FALSE, class.source="bg-success"}
dailydata$ActivityDate <- mdy(dailydata$ActivityDate)

dailydata$Id <- as.character(dailydata$Id)

str(dailydata)
```

## CREATING SUBSET

I believe we have already addressed what needs to be adjusted at this time. If we want to get a deeper analysis into all of the data, it will be much ahead of for a rookie data analyst like me. That is why it is critical to **begin with the simplest scenario first, followed by an update on what I should have done differently with the data**.

As a result, after I converted the data type to the proper one. I'd like to starting the data manipulation process by **producing a subset of the main dataset**.

I began by grouping (aggregating) each piece of data based on their Id and the date.

### Perday Subset

```{r, class.source="bg-success"}
PerDay <- dailydata %>% count(ActivityDate, sort = T)
  
names(PerDay)[2] <- 'User_perday'

PerDay <- dailydata %>% group_by(ActivityDate) %>%
  summarise(total_dailySteps = sum(TotalSteps)
            ,total_dailydistance = sum(TotalDistance)
            ,total_dailycalories = sum(Calories))

PerDay
```

### PerUser Subset

```{r, class.source="bg-success"}
PerUser <- dailydata %>% group_by(Id) %>%
  summarise(UserSteps = sum(TotalSteps)
            ,UserDistance = sum(TotalDistance)
            ,UserCalories = sum(Calories))

PerUser
```

As you can see, I'm simply using three variables at the moment to get a basic overview of the data.

As I was producing this subset, I began to consider how this subject usage time, and the data had already provided me with the information I required.

**That's the exciting part about working as a data analyst**.
Yes, we may begin with some underlying or narrow considerations, but as you dig further into the data, plenty of new problems will arise. It's like a never-ending activity, and there'll always be something fresh if we can put our ideas into action by using the practical capabilities required to realize them.

Enough chit-chat, let's get begin on creating a new subset for part 1 markdown.


## Usage Subset

```{r, class.source="bg-success"}
MinutesUsage <- dailydata %>% 
  select(Id, ActivityDate, VeryActiveMinutes,FairlyActiveMinutes, LightlyActiveMinutes)

head(MinutesUsage)
```

### Based on Date

```{r, class.source="bg-success"}
DailyUsage <- MinutesUsage %>% group_by(Id) %>% 
  summarise(VeryActive = sum(VeryActiveMinutes),FairlyActive = sum(FairlyActiveMinutes)
            ,LightlyActive = sum(LightlyActiveMinutes))

head(DailyUsage)
```

### Based on Id

```{r, class.source="bg-success"}
UsersUsage <- MinutesUsage %>% group_by(ActivityDate) %>%
  summarise(VeryActive = sum(VeryActiveMinutes),FairlyActive = sum(FairlyActiveMinutes)
            ,LightlyActive = sum(LightlyActiveMinutes))

head(UsersUsage)
```

I believe that concludes Part 1 of this series.
We've already created a few necessary subsets, and we'll start plotting in the next section.

for the original data you can access this [link](https://www.kaggle.com/ohseokkim/titanic-hey-machine-tell-me-everything)
or you can just catch me up to my [e-mail](littarizki@gmail.com)

It would be fantastic if you could provide me with some feedback.

Thank you, and I hope to see you again soon!!

**To Be Continue**
